Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Updated running example.

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ stabilizes the closed-loop
system for the discrete plant model $G(z)$.  However, if implementation
aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

@@

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below, which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02634525299072265625\\
\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
\end{array}
$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
\qquad\qquad -0.000213623046875\\
D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
\qquad\qquad -7.2847900390625\\
\end{array}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and we get a new counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02644824981689453125\\
\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
After adding this new counterexample to the set of {\sc inputs}, in the 
next {\sc synthesise} phase, we get a new candidate solution that holds
for both uncertainties in {\sc Inputs}:

$$
\begin{array}{ll}
N_C(z) {=} 7.515781402587890625z^2{-}4.385616302490234375z\\
\qquad\qquad +4.142093658447265625\\
D_C(z) {=} -3.52398681640625z^2{-}1.530254364013671875z \\
\qquad\qquad +7.58094024658203125\\
\end{array}
$$

>>>>

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ stabilizes the closed-loop
system for the discrete plant model $G(z)$.  However, if implementation
aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

@@

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below at $I_b=16,F_b=24$,
which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.026506\\
\Delta D_G(z) = 1.000610z+1.002838
\end{array}
$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
\end{array}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

$$
\begin{array}{ll}
N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
\end{array}
$$
